Approximation as Differentiation

### 2025-06-08 main/first-order.tex
Approximating multiplication.

One might also like to allow the programmer be able to embed additional ``approximation points'' into
composite structures, by providing the language with a \emph{lifting} monad $\syn{L}$. Rather than the usual
definition of $\syn{list}\;\syn{nat}$ as $\mu\alpha.1 + \syn{nat} \times \alpha$, one could then define a type
of ``approximation lists'' $\mu\alpha.\syn{L}\;(1 + \syn{L}\;\syn{nat} \times \alpha)$, along with an
``approximating'' version of multiplication $*: \syn{L}\;\syn{nat} \times \syn{L}\;\syn{nat} \to
\syn{L}\;\syn{nat}$.

>>>>

One might also like to allow the programmer be able to embed additional ``approximation points'' into
composite structures, by providing the language with a \emph{lifting} monad $\syn{L}$. Rather than the usual
definition of $\syn{list}\;\syn{nat}$ as $\mu\alpha.1 + \syn{nat} \times \alpha$, one could then define within
the language a type of ``approximation lists'' $\mu\alpha.\syn{L}\;(1 + \syn{L}\;\syn{nat} \times \alpha)$,
along with an approximating version of multiplication $*_{\text{appr}}: \syn{L}\;\syn{nat} \times
\syn{L}\;\syn{nat} \to \syn{L}\;\syn{nat}$ expressible as
\[x *_{\text{appr}} y = \tmBind{x}{\tmFun{x'}{\syn{if}\;x' =
0\;\syn{then}\;\tmReturn{0}\;\syn{else}\;\tmBind{y}{\tmFun{y'}{\tmReturn{x' * y'}}}}}\].
